Concurrent Programming with CXL

### 2020-06-24 book/paper.tex
Latest

Having the two adjoining nodes locked, implementing \texttt{lst\_insert}
and \texttt{lst\_remove} is straightforward.
The \texttt{lst\_contains} method can simply scan through the list
because the \texttt{next} pointers are updated atomically in such a
way that they always point to a legal suffix of the list.

@@

\section*{Exercises}
\begin{problems}
\item See if you can implement barrier synchronization for $N$ processes
with just three semaphores.  Busy waiting is not allowed.  How about just two?
\end{problems}

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{lv = e} & \texttt{lv} is an lvalue and \texttt{e} is an expression\\
\hline
\texttt{pass} & do nothing\\
\hline
\texttt{del lv} & delete\\
\hline
\texttt{assert b [, x]} & \texttt{b} is a Boolean.  If \texttt{False}, optionally print expression \texttt{e}\\
\hline
\texttt{const v = e} & \texttt{v} is an identifier, \texttt{e} is a constant expression\\
\hline
\texttt{def m(v, ...): S} & \texttt{m} and \texttt{v} are identifiers, \texttt{S} a list of statements\\
\hline
\texttt{let v = e, ...: S} & \texttt{e} is an expression, \texttt{S} a list of statements\\
\hline
\texttt{if b: S} & \texttt{b} is a Boolean, \texttt{S} a list of statements\\
\hline
\texttt{while b: S} & \texttt{b} is a Boolean, \texttt{S} a list of statements\\
\hline
\texttt{for v in e: S} & \texttt{e} is a set evaluated in order,
                            \texttt{S} a list of statements\\
\hline
\texttt{atomic: S} & \texttt{S} a list of statements\\
\hline
\texttt{spawn p e [, t]} & \texttt{p} is a method, \texttt{e} is an expression, \texttt{t} is an optional tag (an expression) \\
\hline
\texttt{go c e} & \texttt{c} is a context, \texttt{e} is an expression \\
\hline
\texttt{import m} & \texttt{m} identifies a module \\
\hline
\end{tabular}
\vspace{1em}

>>>>

Having the two adjoining nodes locked, implementing \texttt{lst\_insert}
and \texttt{lst\_remove} is straightforward.
The \texttt{lst\_contains} method can simply scan through the list
because the \texttt{next} pointers are updated atomically in such a
way that they always point to a legal suffix of the list.
An invariant of the algorithm is that at any point in time the
list is ``complete'', starting with a \texttt{-inf} node and ending
with a \texttt{inf} node.

@@

\section*{Exercises}
\begin{problems}
\item See if you can implement barrier synchronization for $N$ processes
with just three semaphores.  Busy waiting is not allowed.  How about just two?
\item Implement barrier synchronization with Mesa condition variables.
\end{problems}

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{lv = e} & \texttt{lv} is an lvalue and \texttt{e} is an expression\\
\hline
\texttt{lv [op]= e} & op is one of \texttt{+}, \texttt{-}, \texttt{*}, \texttt{/}, 
\texttt{and}, and \texttt{or}\\
\hline
\texttt{pass} & do nothing\\
\hline
\texttt{del lv} & delete\\
\hline
\texttt{assert b [, x]} & \texttt{b} is a Boolean.  If \texttt{False}, optionally print expression \texttt{e}\\
\hline
\texttt{const v = e} & \texttt{v} is an identifier, \texttt{e} is a constant expression\\
\hline
\texttt{def m(v, ...): S} & \texttt{m} and \texttt{v} are identifiers, \texttt{S} a list of statements\\
\hline
\texttt{let v = e, ...: S} & \texttt{e} is an expression, \texttt{S} a list of statements\\
\hline
\texttt{if b: S} & \texttt{b} is a Boolean, \texttt{S} a list of statements\\
\hline
\texttt{while b: S} & \texttt{b} is a Boolean, \texttt{S} a list of statements\\
\hline
\texttt{for v in e: S} & \texttt{e} is a set evaluated in order,
                            \texttt{S} a list of statements\\
\hline
\texttt{atomic: S} & \texttt{S} a list of statements\\
\hline
\texttt{spawn p e [, t]} & \texttt{p} is a method, \texttt{e} is an expression, \texttt{t} is an optional tag (an expression) \\
\hline
\texttt{go c e} & \texttt{c} is a context, \texttt{e} is an expression \\
\hline
\texttt{import m} & \texttt{m} identifies a module \\
\hline
\end{tabular}
\vspace{1em}
